Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-06 paper-1/manuscript.tex
Rev: Stronger F5d conclusion

Correlating the non-target response contrast (\dev{} - \msc{}) with the contrast in $V_{TA}$ across excitatory neurons (Figure \ref{fig5}c), we found that the reduced non-target response magnitude in \dev{} almost perfectly predicted the resulting reduction in TA levels (Pearson's $\rho$ = 0.99).
This finding held across networks and stimuli, as shown in Figure \ref{fig5}d, with a median correlation coefficient of 0.99 and a consistent reduction in the median non-target response between \msc{} and \dev{} sequences (T = 525, p = 2.12e-16, median = -0.094; one-sided Wilcoxon, n = 120), clearly validating our notion that the non-target trial response is the primary driver of TA.

>>>>

Correlating the non-target response contrast (\dev{} - \msc{}) with the contrast in $V_{TA}$ across excitatory neurons (Figure \ref{fig5}c), we found that the reduced non-target response magnitude in \dev{} almost perfectly predicted the resulting reduction in TA levels before target stimuli (Pearson's $\rho$ = 0.99).
This finding held across networks and stimuli, as shown in Figure \ref{fig5}d, with a median correlation coefficient of 0.99 and a consistent reduction in the median non-target response between \msc{} and \dev{} sequences (T = 525, p = 2.12e-16, median = -0.094; one-sided Wilcoxon, n = 120), clearly validating our notion that the reduced non-target trial response was the primary driver of lower TA, which we showed above to be responsible for the higher target response.
